%!TEX root = ./intern_report.tex
\section*{Preface}

\paragraph{}
Described in this report is the 24 week training experience I had in wave computing/Paraqum Technologies dating from 25.06.2018 to 07.12.2018 for the fulfillment of industrial training requirements of my B.Sc. in Electronics and Telecommunication Engineering. The report consists of 3 main sections as follows

\subsubsection*{Chapter 1: Introduction to Wave computing and Paraqum Technologies}
\paragraph{}
Wave computing is a USA based AI startup and Paraqum Technologies is a Sri Lankan Electronic design startup. Wave is now ranked among the top 25 AI providers of the world~\cite{top25ai} and Paraqum Technologies is highly respected in Sri Lanka as a pioneer of the industry and recieves design contracts from all over the world. Our training was done through a design contract offered to Paraqum by Wave computing.

\subsubsection*{Chapter 2: Training Experience}
\paragraph{}
Even though I was an intern, I was given full exposure to the company workflow. I recieved a full scale project to lead and a support team from all over the world to work with. Everyone in the company were very supportive and friendly. The environment was comfortable to work and the workload was perfectly balanced, demanding yet not overwhelming.

\subsubsection*{Chapter 3: Conclusion}
\paragraph{}
I can say without a doubt, this is one of the best training experiences one can get. The University of Moratuwa Industrial training division, the Department of Electronic and Telecommunication Engineering and National Apprentice and Industrial Training Authority (NAITA) together did their best to provide us with an exceptional experience that will be very useful for the future of our careers.

\newpage
\section*{Acknowledgment}

\paragraph{}
I take this chance to show my gratitude towards everyone that helped make this training possible and facilitated my time with it. First of all I should thank the industrial training division of University of Moratuwa and the National Apprentice and Industrial Training Authority (NAITA) for allowing us to get an industrial training of this magnitude and quality during the time of our studies and always looking out for the wellbeing of the trainees.

\paragraph{}
I also would like to thank the administration and staff of Paraqum Technologies, starting with the CEO Dr. Ajith Pasqual, ????General Manager???? Eng. Hasanka Sandujith, Eng. Kasun Tharaka who coordinated the internships and all other staff members who helped in a great many ways to make the training a staggering success. 

\paragraph{}
Last but definitely not least, The staff of the Wave computing team (later separated as Wave computing Sri Lanka) were always dedicated to make the training worthwhile for us. I sincerely thank the Senior Director of Software Engineering division of wave computing Eng. Henrik Esbenson, who visited and supervised us from time to time, General manager of Wave computing Eng. Nuwan Gajaweera, Technical leaders Eng. Upul Ekanayaka and Eng. Binu Amarathunga, My supervisors Eng. Achintha Ihalage, Eng. Omega Gamage and SDK team lead Eng. Dakila Serasinghe and all other staff members of wave computing for everything they did for us.

\vspace*{3cm}

\noindent Chinthana Wimalasuriya,\newline
Undergraduate,\newline
Department of Electronics and Telecommunication Engineering,\newline
University of Moratuwa.