%!TEX root = ./intern_report.tex
\subsection{Training Summary}
\paragraph{}
I worked as a training associate electronic engineer under Wave Computing division of Paraqum technologies, later separated as Wave Computing Sri Lanka. I worked on a single complex project that exposed me to all the aspects of the company.

\paragraph{}
The first part of the project was to develop a code translator to convert codes from python to Waves proprietary WFG format. This project took around two months to complete and it got accepted by the wave engineers. Second part, the simulator was a little more complex and it took around three months to fully build and test. It was also accepted and became a hot topic among the Wave engineering community overseas. Final month was spent on building the DMA engine fo the simulator. At the end of six months, i had finished all the tasks assigned to me and handed over the project in a state that may be further developed by wave later.

\paragraph{}
Getting this project working was challenging on many sides. First, I had to get Familiar with the proprietary DPU technology, which has absolutely no information available online. All the documentation on it was a single pdf file published only for internal usage. After that, there were a number of commercial grade tools such as Jira and Gitlab that had to be learnt from scratch. Then I had to learn how to work with my worldwide team. And after the programs were built, it had to be thoroughly tested according to Wave QA standards before giving them to the test users. As challenging these tasks were, I managed to complete them with the help of the people of Wave computing. As the training ended, I believe that I left a positive impression in the minds of the Wave Computing staff.

\subsection{Self analysis}
\paragraph{}
The project pushed my programming skills to the edge and I learned a lot of new things about How to deliver a commercial grade software product. It also taught me soft skills that i could never learn from the university. I also learned to fit in with the corporate culture and work with people who are decades senior than me. It also helped me realize my position relative to the industry standards and I have recognized the following strengths and weaknesses of myself.

\subsubsection*{Strengths}
\begin{itemize}
    \item Have creative solutions to problems
    \item Can follow a plan or Improvise if necessary
    \item Have a widespread technical knowledge
    \item Can work with a team efficiently
    \item Can understand existing implementations with minimal references
\end{itemize}

\subsubsection*{Weaknesses}
\begin{itemize}
    \item Coding speed can be better
    \item Focus on a single task can be improved further
    \item Need some more knowledge on specialized areas such as Machine learning
\end{itemize}

\subsubsection*{Measures to Overcome weaknesses}
\begin{itemize}
    \item To improve coding speed and focus on a task, I intend to participate online coding competitions and practice codingin my free time.
    \item I also intend to do some specialized online courses on vital subjects.
    \item There is a Yoga practice module in semester 6B which I expect to help in focus issues.
\end{itemize}

\subsection{Verdict on training establishment}
\paragraph{}
As described in section \ref{sec:wavelife}, Wave computing is an organization that prioritizes employee satisfaction, which is no different with interns. The training experience from the work perspective is also perfect. They managed to expose us to the cutting edge of electronics industry while maintaining a very comfortable working experience. I cannot imagine a better way to conduct the industrial training program other than the way Wave Computing managed to pull it off.

\subsection{Verdict on Industrial training program}
\paragraph{}
One of the key requirements when applying for a job nowadays is work experience. The NAITA industrial training program can be described as a perfect method of gaining experience during the degree time itself. It presents students with ample opportunities to define their future at their will. Almost all companies are eager to provide their support for the students in this program and practically everyone gets a good outcome from it. Talking about myself, I can doubtlessly claim that I had an exceptional industrial training experience that was well beyond my expectations.